CPU-Scheduling

### 2024-10-18 Handout/article.tex
added stcf/psjf

Probably the most basic of them all.
The "First In, First Our" is just as the name suggests it. 
Usually we humans know it as first come, first served. 
This policies runs into problems really quickly if the discard the possibility of all tasks requiring the same amount of run time. 
A so called "Convoy Effect" takes place. 
Just imagen how annoying it is, when you're at a store and a family of five cuts into the line in front of you. 
They have two full carts loaded. You have to wait until they finish. 
In addition to that they also send back their kid to get something. 
Wouldn't it be overall much faster if they let you in front, before the cashier starts scanning the items?

@@

\section{Shortest Time-to-Completion (STCF)}

>>>>

Probably the most basic of them all.
The "First In, First Our" is just as the name suggests it. 
Usually we humans know it as first come, first served. 
This policies runs into problems really quickly if the discard the possibility of all tasks requiring the same amount of run time. 
A so called "Convoy Effect" takes place. 
Just imagen how annoying it is, when you're at a store and a family of five cuts into the line in front of you. 
They have two full carts loaded. You have to wait until they finish. 
In addition to that they also send back their kid to get an extra bottle of ketchup. 
Wouldn't it be overall much faster if they let you in front, before the cashier starts scanning the items?

@@

\section{Shortest Time-to-Completion First(STCF)}

If SJF and FIFO are cousins that STCF is the brother.
Here we will make SJF "preemptive", meaning that our cashier can now "save" the state of the previously scanned items. 
Therefore STCF is also called "Preemptive Shortest Job First (PSJF)".
Although the switching costs some time, you'd have to wait anyways until our little boy returns with the ketchup\footnote{If you don't know what I am talking about read Chapter 1.1 (FIFO)}
The option of saving a state comes in handy, especially if a program has to wait for I/O.
Preemptiveness also makes the computer much more response, because now you can really do certain things "at the same time".
The best part is that we don't even have to change much of the previous code.
\pagebreak
\begin{lstlisting}[language=Python, style=colorEX]
  # Simple implementation of STCF in Python

  # definition of client class and list go here
  current = Client(ttc)
  current_runtime = 0

  # Adding a new process
  def add_client(client): 
    list.append(client)
    allocate()

  # Decide which process is next
  def allocate():
    save_state() # saves of the current process

    current.ttc -= current_runtime # first update ttc
    current_runtime = 0

    list.sort(key=lambda a: a.ttc) # sort according to ttc
    current = list.pop(0)

    use_resource(current) # function that will allow "next" to use the CPU (also tracks runtime)
\end{lstlisting}
IDK ABOUT THE CODE; IT IS JUST KINDA HACKED TOGETHER; IT IS DEFINITELY NOT SECURE WHATSOEVER! 
Whenever a new client "joins", the "allocation" function gets run.
In addition to that, whenever the process finishes, or it voluntarily gives up the CPU, the same "allocation" function can be run.
